Geometric variational problems

### 2020-11-05 NSF2020/Description/specificaim1_ver2.tex
...

\newpage

@@

The elastic theory assumes an energy density that is quadratic in the Green-Lagrange strain tensor for $x$. 
The chains stretch and compress to satisfy incompressibility.
Symmetries with respect to mirror reflection and in-plane rotation, the internal structure assumptions and incompressibility
lead to an elastic surface energy over the dividing surface $\Sigma$. 
This energy decomposes into four, fundamental and independent deformations:
splay ($\Div n$), twist ($\Curl n$), saddle splay ($\det \nabla n$) and tilt $T$:
\begin{equation}
\label{ansatz3}
\begin{aligned}
\int_{\Sigma} 
  \tfrac{1}{2}\KB\left[ \left( \Div n + k_0\right)^2 - k_0^2\right] 
+ \tfrac{1}{2}\KT (\Curl n)^2 + \KG  \det \nabla n + \KTH |T|^2 \,dA.
\end{aligned}
\end{equation}
Here $\Div n$, $\Curl n$ and $\nabla n$ refer to the surface divergence, surface curl and surface gradient operators
respectively (Figure \ref{fig:distortions}A--C).
The deformations come with elastic coefficients: the bending modulus $\KB$, twist modulus $\KT$ 
and saddle-splay modulus $\KG$ and tilt modulus $\KTH$
HK define the tilt vector $T = n/(N\cdot n) - N$ where $N$ is the unit surface normal.

@@

\newpage

Specific Aim 1 dealt with the collective material property of amphiphiles which does not involve the movement  of the solvent.
In Specific Aim 2, we include hydrodynamics effects. The reason for including hydrodynamic effects is that 
biologically relevant functions like fusion, fission, pore dynamics involve viscous dissipation of the aqueous environment. 
Moreover, including hydrodynamics adds relevance to our theory since most coarse-grained and molecular dynamics theories
include water either explicitly or implicitly in their models.

>>>>

@@

The elastic theory assumes an energy density that is quadratic in the Green-Lagrange strain tensor for $x$. 
The chains stretch and compress to satisfy incompressibility.
Symmetries with respect to mirror reflection and in-plane rotation, the internal structure assumptions and incompressibility
lead to an elastic surface energy over the dividing surface $\Sigma$. 
This energy decomposes into four, fundamental and independent deformations:
splay ($\Div n$), twist ($\Curl n$), saddle splay ($\det \nabla n$) and tilt $T$:
\begin{equation}
\label{ansatz3}
\begin{aligned}
\int_{\Sigma} 
  \tfrac{1}{2}\KB\left[ \left( \Div n + k_0\right)^2 - k_0^2\right] 
+ \tfrac{1}{2}\KT (\Curl n)^2 + \KG  \det \nabla n + \tfrac{1}{2}\KTH |T|^2 \,dA.
\end{aligned}
\end{equation}
Here $\Div n$, $\Curl n$ and $\nabla n$ refer to the surface divergence, surface curl and surface gradient operators
respectively (Figure \ref{fig:distortions}A--C).
The deformations come with elastic coefficients: the bending modulus $\KB$, twist modulus $\KT$ 
and saddle-splay modulus $\KG$ and tilt modulus $\KTH$
HK define the tilt vector $T = n/(N\cdot n) - N$ where $N$ is the unit surface normal.

@@

### 2020-11-05 NSF2020/Description/specificaim2_ver2.tex
...

%\subsection{Specific Aim 2: Functional Materials}
\subsection{Specific Aim 2: Hydrodynamics and ...}
\label{subsec:specific_aim_2}
%The mathematics of this proposal investigates how three-dimensional solids deform under long-range surface tension interaction. The results generalize the physical principles used in the design of functional materials, enabling investigators to simulate sub-micron scale systems that are otherwise impractical to realize experimentally. It supplies new insight into organizational principles in physical and biological sciences. 
%
Over the past decade, there has been an explosion of interest in the fabrication of complex microscopic three-dimensional structures 
\cite{Cho2010}. These fabrication processes utilize the fact that at small scales, capillary forces dominate  van der Waals interactions and thermal noise  \cite{Zhang2017}, enabling the coordinated movement and binding of material subunits. Two prominent fabrication techniques are capillary origami 
\cite{Pandey2011,Leong2007,Reynolds2019} and colloidal self-assembly \cite{Dasgupta2017,Siontorou2017}. Capillary origami uses principles of elastocapilirity wherein elastic solids deform under surface tension \cite{Bico2018,VanHonschoten2010}. In self-assembly of colloids, 
particles exhibit similar thermodynamic behavior of molecular systems, except that the behavior occurs over observable, long time scales \cite{Zhang2017}.

>>>>

%\subsection{Specific Aim 2: Functional Materials}
\subsection{Specific Aim 2: Hydrodynamics and ...}
\label{subsec:specific_aim_2}
Specific Aim 1 dealt with the collective material property of amphiphiles which does not involve the movement  of the solvent.
In Specific Aim 2, we include hydrodynamics effects. The reason for including hydrodynamic effects is that 
biologically relevant functions like fusion, fission, pore dynamics involve viscous dissipation of the aqueous environment. 
Moreover, including hydrodynamics adds relevance to our theory since most coarse-grained and molecular dynamics theories
include water either explicitly or implicitly in their models.

%The mathematics of this proposal investigates how three-dimensional solids deform under long-range surface tension interaction. The results generalize the physical principles used in the design of functional materials, enabling investigators to simulate sub-micron scale systems that are otherwise impractical to realize experimentally. It supplies new insight into organizational principles in physical and biological sciences. 
%
Over the past decade, there has been an explosion of interest in the fabrication of complex microscopic three-dimensional structures 
\cite{Cho2010}. These fabrication processes utilize the fact that at small scales, capillary forces dominate  van der Waals interactions and thermal noise  \cite{Zhang2017}, enabling the coordinated movement and binding of material subunits. Two prominent fabrication techniques are capillary origami 
\cite{Pandey2011,Leong2007,Reynolds2019} and colloidal self-assembly \cite{Dasgupta2017,Siontorou2017}. Capillary origami uses principles of elastocapilirity wherein elastic solids deform under surface tension \cite{Bico2018,VanHonschoten2010}. In self-assembly of colloids, 
particles exhibit similar thermodynamic behavior of molecular systems, except that the behavior occurs over observable, long time scales \cite{Zhang2017}.
